Formalizing Stack Safety as a Security Property

### 2021-07-07 submission3/main.tex
Nit

\bcp{Have we made the diagrams comprehensible when printed in
  B/W or viewed by a colorblind person?  If so we should say that the colors
are just extra hints.}%
Colored boxes indicate an assignment of the address to a
{\em domain}---a label reflecting a particular set of intended access
rights.\bcp{should we say here that it is the job of an enforcement mechanism to
  manage and enforce these access permissions?} Domains
are \(\unsealed\) (in the stack and accessible to writes), \(\sealed{\depth}\)
(in the stack and reserved for the caller at depth \(\depth\)), and \(\outside\)
(outside the stack entirely.) These are abbreviated \(U\) and \(S(\dots)\) in the
figures. For our purposes, \(\outside\) will apply to global
variables and code. Domains are part of the {\em context} of a machine state.
(We will introduce some other parts of the context as needed.)

>>>>

\bcp{Have we made the diagrams comprehensible when printed in
  B/W or viewed by a colorblind person?  If so we should say that the colors
are just extra hints.}%
Colored boxes indicate an assignment of the address to a
{\em domain}---a label reflecting a particular set of intended access
rights.\bcp{should we say here that it is the job of an enforcement mechanism to
  manage and enforce these access permissions?} Such a domain 
can be \(\unsealed\) (in the stack and accessible to writes), \(\sealed{\depth}\)
(in the stack and reserved for the caller at depth \(\depth\)), or \(\outside\)
(outside the stack entirely.) These are abbreviated \(U\) and \(S(\dots)\) in the
figures\leo{No outside?}. For our purposes, \(\outside\) will apply to global
variables and code. Domains are part of the {\em context} of a machine state.
(We will introduce some other parts of the context as needed.)
